Uncertainty Quantification in Multiscale Models of Charge Transport in Organic Semiconductors: Influence of the Exhange-Correlation Functional

### 2025-01-27 paper.tex
cleaned up

This paper is organized as follows. Section~\ref{sec:model} outlines the theoretical and computational details of the multiscale model, including the morphology simulation with classical molecular dynamics, the determination of all quantities in the transition rates, and the calculation of the charge transport properties from the constructed graph model. In Section~\ref{sec:MSMresults}, we discuss the explicit results from the model using different values of $\alpha_\text{HFX}$, before we show the results of uncertainty quantification and sensitivity analysis via Monte Carlo sampling. A brief summary concludes the paper.

>>>>

This paper is organized as follows. Section~\ref{sec:model} outlines the theoretical and computational details of the multiscale model, including the morphology simulation with classical molecular dynamics, the determination of all quantities in the transition rates, and the calculation of the charge transport properties from the constructed graph model. In Section~\ref{sec:MSMresults}, we discuss the explicit results from the model using different values of $\alpha_\text{HFX}$, before we show the results of uncertainty quantification and sensitivity analysis via Monte Carlo sampling in Section~\ref{sec:UQ}. A brief summary concludes the paper.
